\addcontentsline{toc}{chapter}{Список литературы}
\begin{thebibliography}{99}  
\bibitem{zheng-ming} Zheng-ming L. // Phys. Rev. B: Condens. Matter. 1985. V.32. No2. P. 824.
    
\bibitem{smolar} Smolar V.// Vacuum. 1994. V. 45. No6. P. 609.
   
\bibitem{mikheev} Михеев Н. П., Смоляр В.А.// УФЖ. 1985. Т.30. No1. С. 140.
    
\bibitem{smolar1} Смоляр В.А. // УФЖ. 1988. Т. 33. No 7. С. 1072.
    
\bibitem{smolar2} Smolar V.// Vacuum. 1990. V. 41. No7–9. P. 1718.
    
\bibitem{keiz} Кейз К., Цвайфель П. Линейная теория переноса. М.: Мир,. 1972.
    
\bibitem{korn} Корн Г., Корн Т. Справочник по математике для научных работников и инженеров. М.: Наука, 1968.
    
\bibitem{smolar3} Смоляр~В.~А.// УФЖ. 1982. Т. 27. No 10. С. 1537.
    %литра с дипломника
    
\bibitem{1} Reimer. SEM. Physics of Image Formation and Microanalysis
    
\bibitem{2} ``Практическая растровая электронная микроскопия'', под ред.
Гоулдстейна Дж. и Яковца Х. М.: Мир, 1978
    
\bibitem{3} А.В. Заблоцкий, А.С. Батурин, Е.А. Тишин, А.А. Чуприк.
``Растровый электронный микроскоп: Лабораторная работа''. – М.:
МФТИ, 2007. – 52 с.
    
\bibitem{4} D. F. Kyser and N. S. Viswanathan. "Monte Carlo simulation of spatially
distributed beams in electron-beam lithography," Journal of Vacuum
Science \& Technology B, vol. 12 No6, p. 1305-1308 (1975).
    
\bibitem{5} P. M. Mankewich, L. D. Jackel, and R. E. Howard. ``Measurements of
electron range and scattering in high voltage e-beam lithography'',
Journal of Vacuum Science \& Technology B, vol. 3 No3, p. 174-176
(1985).
    
\bibitem{6} D. Chow, J. McDonald, D. King, W. Smith, K. Molnair, and A. Steckl.
``An image processing approach to fast, efficient proximity correction for
electron beam lithography'', Journal of Vacuum Science \& Technology
B, vol. 1 No4, p. 1383-1390 (1983).
    
\bibitem{7} V. V. Aristov, B. N. Gaifullin, A. A. Svintsov, S. I. Zaitsev, R. R. Jede
and H.F. Raith. ``Accuracy of proximity correction in electron
lithography after development'', Journal of Vacuum Science \&
Technology B, vol. 10 No 6, p. 2459-2467 (1992).
    
\bibitem{8} V. V. Aristov, A. A. Svintsov and S. I. Zaitsev. ``Guaranteed accuracy of
the method of ‘simple’ compensation in electron lithography'',
Microelectronic Engineering, vol. 11 Issues 1-4, p. 641-644 (1990).
    
\bibitem{9} S.V. Dubonos, B.N. Gaifulin, H.F. Raith, A.A. Svintsov, and S.I. Zaitsev,
Microelectron. Eng. 21, 293 (1993)
    
\bibitem{10} (3-1) Друкарёв Г.Ф. «Столкновение электронов с атомами и
молекулами» 1978 М. «Наука»
39
    
\bibitem{11} (3-18)D. C. Joy, ``Monte Carlo Modeling for Electron Microscopy and
Microanalysis'', Oxford University Press, 1995.
    
\bibitem{12} (3-4) Бёте «Квантовая механика»
    
\bibitem{13} (3-5) Л.Д. Ландау Е.М. Лившиц «Теоретическия физика. Том III.
Квантовая механика. Нерелятивистская теория» 1989 М. Наука.
    
\bibitem{14} C. A. Deckert and D. A. Peters. ``Optimization of thin film wetting and
adhesion behavior'', Thin solid films, vol. 68 Issue 2, p. 417-420 (1980).
    
\bibitem{15} У. Моро, ``Микролитография. Принципы, методы, материалы''//
«Мир», (1990).
    
\bibitem{16} P. D. Blais. ``Edge acuity and resolution in positive type photo-. resist
systems''// Solid-state Technol., vol. 20, p. 76-79 (1977).
    
\bibitem{17} H. Frish. ``Sorption and transport in glassy polymers-a review''// Polym.
Eng. Sci., vol. 20 Issue 1, p. 2-13 (1980).
    
\bibitem{18} S. Chen and J. Edin. ``Fickian diffusion of alkanes through glassy
polymers: Effects of temperature, diffusant size, and polymer structure''//
Polym. Eng. Sci., vol. 20, p. 40-50 (1980).
    
\bibitem{19} G. Park. ``Diffusion in Polymers''// edited by J. Crank and G. Park,
Academic Press, New York, Chapter 5, p. 140-162 (1968).
    
\bibitem{20} L. Thomas and J. Windle. ``A theory of case II diffusion''// Polymer, vol.
23 Issue 4, p. 529-542 (1982).
    
\bibitem{21} K. Ueberreiter. ``Diffusion in Polymers''// edited by J. Crank and G. Park, ``Academic Press'', New York, , Chapter 5, p. 219-257 (1968).
    
\bibitem{22} K. Ueberreiter and F. Asmussen. ``Velocity of dissolution of
polystyrene''// J. Pol. Sci., vol. 23 Issue 103 , p. 75-81 (1957).
    
\bibitem{23} ``Handbook of Microlithography, Micromachining and Microfabrication''// edited by P. Rai-Choudhury, SPIE, Chapter 2, (1997).

\end{thebibliography}
