\addcontentsline{toc}{chapter}{Список использованных источников}
\def\bibname{СПИСОК ИСПОЛЬЗОВАННЫХ ИСТОЧНИКОВ}
\begin{thebibliography}{99}
\newcommand{\tabfix}{\hspace*{1.25cm}}
\bibitem{zheng-ming} \tabfix Zheng-ming,~L. Improved bipartitition model of electron
transport. II. Application to inhomogeneoue media / L.~Zheng-ming // Phys. Rev. B:
Condens. Matter. -- 1985. Vol.~32, N~2. -- P.~824--836.

\bibitem{smolar} \tabfix Smolar,~V. Backscattering and transmission for normal
incidence of electrons in small-angle and transport approximation /
V.~Smolar // Vacuum. 1994.~-- Vol.~45, N~6.~-- P.~609--615.

\bibitem{mikheev} \tabfix Михеев,~Н.~П. Транспортно-диффузионное приближение в теории
переноса электронов / Н.~П.~Михеев, В.~А.~Смоляр.~// Украинский физический
журнал.~-- 1985.~-- Т.~30, вып.~1.~-- С.~140--143.

\bibitem{smolar1} \tabfix Смоляр,~В.~А. Транспортно-малоугловое приближение в теории
переноса электронов средних энергий / В.~А.~Смоляр.~// Украинский физический
журнал.~-- 1988.~-- Т.~33, вып.~7.~-- С.~1072--1077.

\bibitem{smolar2} \tabfix Smolar,~V. Electron backscattering and penetration in the
small-angle and transport approximation model / V.~Smolar.~// Vacuum.~-- 1990.~--
Vol.~41, N~7--9.~-- P.~1718.--1720.

\bibitem{keiz} \tabfix Кейз,~К. Линейная теория переноса / К.~Кейз, П.~Цвайфель //
М.:~Мир, 1972 // 384~c.

\bibitem{korn} \tabfix Корн,~Г. Справочник по математике для научных работников и
инженеров /  Г.~Корн, Т.~Корн // М.:~Наука, 1968 // 720~c.

%\bibitem{smolar3} \tabfix Смоляр,~В.~А. / В.~А.~Смоляр.~// Украинский физический журнал.
%1982. Т.~27, вып.~10.~-- С.~1537. % не нашел статью

%литра с дипломника

\bibitem{1} \tabfix Reimer,~L. Scanning Electron Microscopy: Physics of Image Formation
and Microanalysis. / L.~Reimer.~-- N.~Y.~:~Springer, 2010 // 527~p.

\bibitem{2} \tabfix Практическая растровая электронная микроскопия / под ред.
Дж.~Гоулдстейна, Х.~Яковица // М.:~Мир, 1978 // 656~с.

\bibitem{3} \tabfix Растровый электронный микроскоп : учеб // метод. пособие /
А.~В.~Заболоцкий А.С. [и др.] // М.:~Изд-во~МФТИ, 2007 //
52~с. %Батурин, Е.А. Тишин, А.А. ЧуприкЪ

\bibitem{4} \tabfix Kyser,~D.~F. Monte Carlo simulation of spatially
distributed beams in electron-beam lithography / D.~F.~Kyser,
N.~S.~Viswanathan.~// Journal of Vacuum Science \& Technology B. 1975 V.~12,
N~6.~-- P.~1305--1308.

\bibitem{5} \tabfix Mankewich,~P.~M. Measurements of electron range and scattering in
high voltage e-beam lithography / P.~M.~Mankewich, L.~D.~Jackel,
R.~E.~Howard.~// Journal of Vacuum Science \& Technology B. 1985. V.~3, N~3.
P.~174--176.

\bibitem{6} \tabfix An image processing approach to fast, efficient proximity correction for
electron beam lithography / D.~Chow, [и др.] ~// Journal of Vacuum Science \& Technology B. 1983.
V.~1, N~4.~-- P.~1383--1390.%J.~McDonald, D.~King, W.~Smith,
%K.~Molnair, A.~Steckl.

\bibitem{7} \tabfix Accuracy of proximity correction in electron lithography after
development / V.~V.~Aristov, [и др.]~// Journal of Vacuum Science \& Technology B. V.~10,
N~6.~-- P.~2459--2467.
%B.~N.~Gaifullin, A.~A.~Svintsov, S.~I.~Zaitsev,
%R.~R.~Jede, H.~F.~Raith.
\bibitem{8} \tabfix Aristov,~V.~V. Guaranteed accuracy of the method of <<simple>>
compensation in electron lithography / V.~V.~Aristov, A.~A.~Svintsov,
S.~I.~Zaitsev.~// Microelectronic Engineering. 1990. V.~11, Is.s~1--4.
P.~641--644.

\bibitem{9} \tabfix Evaluation, verification and error determination of proximity
parameters (alpha, beta and eta) in electron beam lithography / S.~V.~Dubonos [и~др.]~// Microelectronic
Engineering. 1993. V.~21.~-- P.~293--296.%,
%B.~N.~Gaifullin, H.~F.~Raith, A.~A.~Svintsov, S.~I.~Zaitsev.

\bibitem{10} \tabfix Друкарёв,~Г.~Ф. Столкновение электронов с атомами и молекулами /
Г.~Ф.~Друкарёв // М.:~Наука, 1978 // 255~с.

\bibitem{11} \tabfix Joy,~D.~C. Monte Carlo Modeling for Electron Microscopy and
Microanalysis / D.~C.~Joy // Oxford University Press, 1995 // 224~p.

\bibitem{12} \tabfix Бёте,~Г. Квантовая механика / Г.~Бёте // М.:~Мир, 1965 // 333~с.

\bibitem{13} \tabfix Ландау,~Л.~Д. Курс теоретической физики : учеб. пособ. для вузов.
В 10 т. Том III. Квантовая механика (нерелятивистская теория) / Л.~Д.~Ландау, Е.~М.~Лившиц.~--
6-е~изд.,~испр. М.:~Физматлит, 2004 // 800~с.

\bibitem{14} \tabfix Deckert,~C.~A. Optimization of thin film wetting and adhesion
behavior / C.~A.~Deckert, D.~A.~Peters.~// Thin solid films. 1980. Vol.~68,
Is.~2.~-- P.~417--420.

\bibitem{15} \tabfix Моро,~У. Микролитография. Принципы, методы, материалы. В 2 т. / У.~Моро // М.:~Мир, 1990 // 1240~с.

\bibitem{16} \tabfix Blais,~P.~D. Edge acuity and resolution in positive type photo-.
resist systems / P.~D.~Blais~ // Solid-state Technologies. 1977. Vol.~20.~--
P.~76--79.

\bibitem{17} \tabfix Frish,~H. Sorption and transport in glassy polymers-a review /
H.~Frish.~// Polymer Engineering \& Science. 1980. Vol.~20, Is.~1.~-- P.~2--13.

\bibitem{18} \tabfix Chen,~S. Fickian diffusion of alkanes through glassy polymers:
Effects of temperature, diffusant size, and polymer structure / S.~Chen,
J.~Edin.~// Polymer Engineering \& Science. 1980. V.~20, Is.~1.~-- P.~40--50.

\bibitem{19} \tabfix Park,~G. Diffusion in Polymers / G.~Park; edited by J. Crank.~--
N.~Y.:~Academic Press, 1968.~-- 162p.

\bibitem{20} \tabfix Thomas,~L. A theory of case II diffusion / L.~Thomas,
J.~Windle.~// Polymer.~-- 1982.~-- Vol.~23, Is.~4.~-- P.~529--542.

\bibitem{21} \tabfix Ueberreiter,~K. Diffusion in Polymers / K.~Ueberreiter; edited by
J.~Crank, G.~Park.~-- N.~Y.~:~Academic Press, 1968.~-- 257p.

\bibitem{22} \tabfix Ueberreiter,~K. Velocity of dissolution of polystyrene /
K.~Ueberreiter, F.~Asmussen~// Journal of Polymer Science. 1957. Vol.~23,
Is.~103.~-- 81p.

\bibitem{23} \tabfix Handbook of Microlithography, Micromachining and Microfabrication
/ edited by P.~Rai-Choudhury // Washington:~SPIE Press, 1997 // 768~p.

\end{thebibliography}
